Avoiding accuracy-limiting pitfalls in the study of protein-ligand interactions with isothermal titration calorimetry

### 2016-01-04 manuscript/itc-worksheet.tex
Fix 10 ug -> 10 mg

We chose to prepare a 1~500 $\mu$M CBS stock solution as a compromise between ensuring complete solubility of CBS (solubility 2 250 $\mu$M in water) and minimizing buffer use (preparing a solution of $\sim$720 $\mu$M directly with 10 $\mu$g CBS would have doubled the quantity of buffer required).
To do this, we added 10.0(1) mg CBS to 32.1(2) mL PBS dialysate and vortexed to ensure the compound was completely dissolved, yielding 32.2(2) mL of a 1.50(2) mM CBS stock solution.

>>>>

We chose to prepare a 1~500 $\mu$M CBS stock solution as a compromise between ensuring complete solubility of CBS (solubility 2 250 $\mu$M in water) and minimizing buffer use (preparing a solution of $\sim$720 $\mu$M directly with 10 mg CBS would have doubled the quantity of buffer required).
To do this, we added 10.0(1) mg CBS to 32.1(2) mL PBS dialysate and vortexed to ensure the compound was completely dissolved, yielding 32.2(2) mL of a 1.50(2) mM CBS stock solution.
